Timeliness of security updates for Android

### 2014-10-30 securityupdates.tex
Cut a bunch of stuff and put in a cutting floor section at the end as we may want people to suggest we put them back.

In the past users of Microsoft IIS were advised to switch to a different web server due to the frequent discovery of vulnerabilities~\cite{Pescatore2001}.
This pressure encouraged Microsoft to improve the security of their products~\cite{TODO}.
Part of the reason why deployed devices do not receive updates in a timely manner is that there is little data on what is actually happening and so it is not possible to determine which manufacturers or operators are doing a better job.
Hence there is little incentive for manufacturers and operators to do a better job.
We provide this data  in~\S\ref{sec:security_scoring} and discuss incentives further in \S\ref{sec:economics}.

The contributions of this paper are:
\begin{itemize}
 \item We characterise the Android update ecosystem and quantify its vulnerability to root equivalent vulnerabilities.
 \item We collate information on vulnerabilities which affect Android and investigate their time-lines.
 \item We measure the security of Android according to three metrics and compare different manufacturers. and device models to allow consumers to differentiate between them based on security.
 \item We provide models of how the distribution of Android versions changes allowing future version distributions to be predicted.
% \item We propose methods which could be used to improve the situation in future.
\end{itemize}

@@

\section{Experiments}
\label{sec:results}
We present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root equivalent vulnerabilities on average.
On average only \daUpdatesPerYear\ updates reach a device each year and \daPercUpdatesDowngrades\ of version changes are downgrades to older versions.
Nexus devices are better than others, \emph{\daSecScoreBestmanufacturer} to be the best manufacturer and \emph{\daSecScoreBestoperator} to be the best network operator and modelling the uptake of new versions of Android.
%\todo{comparison of nexus update rates with iOS}
We conducted four experiments examining the behaviour of the Android ecosystem as a whole (\S\ref{sec:exp:android_ecosystem}), updates reaching particular devices (\S\ref{sec:exp:device_updates}), comparisons between different manufacturers and operators (\S\ref{sec:exp:security_score}) and model how long it will take for an update to be fixed once an update is released (\S\ref{sec:exp:predicting_distributions}).

@@

>>>>

In the past users of Microsoft IIS were advised to switch to a different web server due to the frequent discovery of vulnerabilities~\cite{Pescatore2001}.
This pressure encouraged Microsoft to improve the security of their products~\cite{TODO}.
Part of the reason why deployed devices do not receive updates in a timely manner is that there is little data on what is actually happening and so it is not possible to determine which manufacturers or operators are doing a better job.
Hence there is little incentive for manufacturers and operators to do a better job.
We provide this data  in~\S\ref{sec:security_scoring}.

The contributions of this paper are:
\begin{itemize}
 \item We characterise the Android update ecosystem and quantify its vulnerability to root equivalent vulnerabilities.
 \item We collate information on vulnerabilities which affect Android and investigate their time-lines.
 \item We measure the security of Android according to three metrics and compare different manufacturers. and device models to allow consumers to differentiate between them based on security.
\end{itemize}

@@

\section{Experiments}
\label{sec:results}
We present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root equivalent vulnerabilities on average.
On average only \daUpdatesPerYear\ updates reach a device each year and \daPercUpdatesDowngrades\ of version changes are downgrades to older versions.
Nexus devices are better than others, \emph{\daSecScoreBestmanufacturer} to be the best manufacturer and \emph{\daSecScoreBestoperator} to be the best network operator and modelling the uptake of new versions of Android.
%\todo{comparison of nexus update rates with iOS}
We conducted three experiments examining the behaviour of the Android ecosystem as a whole (\S\ref{sec:exp:android_ecosystem}), updates reaching particular devices (\S\ref{sec:exp:device_updates}) and comparisons between different manufacturers and operators (\S\ref{sec:exp:security_score}).

@@

\listoftodos

\section{Cutting floor}

This section contains things which we were intending to include but which have not made the cut.
